Making Deep Q-learning Methods Robust to Time Discretization

### 2019-01-19 paper/icml_drau/framework.tex

% TODO: For now, differential equation is the default, SDE is a footnote.
Let ${\cal S} = \mathbb{R}^d$ be a set of states, and ${\cal A}$ be a set of
actions. Consider the continuous \emph{Markov Decision Process} (MDP) defined by the differential equation %\TODO{Explain the intuition of Brownian in SDE}:
        \begin{equation}
	\label{eq:diffusion}
	ds = F(s, a)dt. % + \Sigma(s, a)\dbt.
              \end{equation}
        For any $\deltat$, the discrete MDP ${\cal
M}_\deltat = \langle {\cal S}, {\cal A}, T_{\deltat}, r_\deltat,
      \gamma_\deltat\rangle$ is a discretization of the continuous MDP with
      \emph{time discretization} $\deltat$. Here the deterministic
      transition function
      $T_\deltat(s, a, s')$ is %a dirac on $s_\deltat$, where $s_\deltat$ is 
      the
      state obtained
      when starting at $s_0 = s$ and maintaining $a_t=a$ constant for a time
      $\deltat$.
      This corresponds to an agent evolving in the continuous
      environment \eqref{eq:diffusion}, but 
      only making observations and choosing actions every $\deltat$. We
      call such an  MDP ${\cal M}_\deltat$
      \emph{near-continuous}.\footnote{
      We believe the results presented here hold more
      generallly, assuming states
      follow a \emph{stochastic} differential equation \begin{equation}
	      ds = F(s, a)dt  + \Sigma(s, a)\dbt
	      \label{eq:sde}
      \end{equation} with
      $B_t$ a multidimensional Brownian motion and $\Sigma$ a covariance matrix. A
      formal treatment of SDEs is beyond the scope of this paper.}
      Informally $F: {\cal S}\times{\cal A}\rightarrow {\cal S}$ describes
the dynamic of the environment. The agent interacts with the environment through a deterministic policy function
$\pi \colon {\cal S} \rightarrow {\cal A}$. Determinism of the policy is assumed to prevent problematic definitions
of the value function in continuous time. This is only a mild requirement, as we introduce an off-policy algorithm,
and only impose determinism of the exploitation policy.
% This framework covers classical control theory, as well as many usual simulated environments. TODO: not convinced that this is relevant here.

>>>>

% TODO: For now, differential equation is the default, SDE is a footnote.
Let ${\cal S} = \mathbb{R}^d$ be a set of states, and ${\cal A}$ be a set of
actions. Consider the continuous \emph{Markov Decision Process} (MDP) defined by the differential equation %\TODO{Explain the intuition of Brownian in SDE}:
        \begin{equation}
	\label{eq:diffusion}
	ds = F(s, a)dt. % + \Sigma(s, a)\dbt.
              \end{equation}
Informally, $F\colon {\cal S}\times{\cal A}\rightarrow {\cal S}$ describes
the dynamics of the environment. The agent interacts with the environment through a deterministic policy function
$\pi \colon {\cal S} \rightarrow {\cal A}$, so that $a=\pi(s)$. 
For simplicity we assume here that both the dynamics and exploitation policy are
deterministic; the exploration policy will be random, but care must be
taken to properly define random policies with
discrete actions in continuous time, see below.

For any $\deltat>0$, we can define an MDP ${\cal
M}_\deltat = \langle {\cal S}, {\cal A}, T_{\deltat}, r_\deltat,
      \gamma_\deltat\rangle$ as a discretization of the continuous MDP with
      \emph{time discretization} $\deltat$. Here the deterministic
      transition function
      $T_\deltat(s, a, s')$ is %a dirac on $s_\deltat$, where $s_\deltat$ is 
      the
      state obtained
      when starting at $s_0 = s$ and maintaining $a_t=a$ constant for a time
      $\deltat$.
      This corresponds to an agent evolving in the continuous
      environment \eqref{eq:diffusion}, but 
      only making observations and choosing actions every $\deltat$. The
      rewards and decay factor are specified below. We
      call such an  MDP ${\cal M}_\deltat$
      \emph{near-continuous}.\footnote{
      We believe the results presented here hold more
      generallly, assuming states
      follow a \emph{stochastic} differential equation \begin{equation}
	      ds = F(s, a)dt  + \Sigma(s, a)\dbt
	      \label{eq:sde}
      \end{equation} with
      $B_t$ a multidimensional Brownian motion and $\Sigma$ a covariance matrix. A
      formal treatment of SDEs is beyond the scope of this paper.}
      % This framework covers classical control theory, as well as many usual simulated environments. TODO: not convinced that this is relevant here.
